Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations 

### 2022-01-21 paper2.Rmd
Data section done

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra)

@@

# Intro
It is unclear how individuals choose to search for information through the
multimedia environment of the 21st century. Much of the research conducted in
social networks and communication focus on senders, influencers, and persuasion
strategies (Merton 1968) rather than on “the receiver as an active information
seeker and processor. " (Johnson and Meischke 1993).

Core discussion networks are the default lens to investigate network resources
and social support in surveys. The underlying assumption is that individuals
reach out to a handful of strong ties when in need of support, which can be
elicited in surveys using name generators (Marsden 1987). This approach has
yielded important insights, but largely overlooks crucial processes of resource
activation (Hurlbert, Haines, and Beggs 2000; Perry and Pescosolido 2015; Smith
2005). Small (2017) shows that the core discussion network does not capture how
people activate social support in practice and indicates that people draw on
much broader social connections for support, also calling back to the weak ties
research by Granovetter (1973). There is ongoing research investigating how
weak-tie support holds for different support types based on the architecture put
forward by House, Umberson, and Landis (1988) of instrumental, emotional, and
informational support (Legewie and Gonzalez 2020). I follow the definition of
Cohen and Wills (1985) and define informational support as “help in defining,
understanding,  and coping with problematic events and include education,
advice, or referral to another source of  support” (Winemiller et al. 1993:640).

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
*f the most convenient vehicles for information search. While Small (2017)
focuses on how support can depend on a network tie simply "happened to be
there", online search is theoretically the most frictionless and costless mode
*f support. There are three computer-mediated vehicles I consider for this
analysis: search engines like Google, posting questions on online forums like
subreddits or Facebook groups, and posting a status update online via Facebook
*r Twitter. The first two comprise what I call “online search”, while the third
is conceptually distinct and important to include in the survey; yet, it is a
hybrid of social network activation and online search.

@@

For this paper, I will use the case of Covid-19 vaccinations to explore the
variation among information search vehicles. There are theoretical reasons why
individuals would choose to search for information among their network ties
instead of online search. For instance, Rains (2018) finds that patients tend to
search for technical information about an illness online but turn to their
social network for experiential information from others facing similar
circumstances in the case of cancer. Moreover, if an individual distrusts the
medical establishment, or popular media, they may be more likely to activate
informational support among their social network or turn to online groups that
validate their worldview (Bogers and Wernersen 2014).

This research project is important because the vehicles used to search by people
impacts the information they are exposed to. Given the large swaths of both
misinformation and disinformation regarding Covid-19 (Motta, Stecula, and
Farhart 2020; Pathak, Agarawalla, and Gupta 2020; Shahsavari et al. 2020) and
the measurable impacts this misinformation has had on pandemic-related health
behaviors, how we choose to search for information affects our own lives and the
lives of others. Moreover, individuals who do not utilize social networks for
information search may feel like they have no network support, leading to
feelings of network isolation with major implications for mental health (Thoits
2011).

@@

# Research Methodology
The data used for this research project are based on original survey data sampled between `r format( min(rain$date), '%B %d, %Y')`  through `r format(max(rain$date), '%B %d, %Y')`.
- grant sample
- MTurk
- Dates 
- Locations

## Descriptive Statistics

###  Dependent Variables 
search for info
int_sought_

search for info by type
int_sought_fr_pers  
int_sought_fr_dr    
int_sought_fr_onlgroup
int_sought_fr_onlnet
int_sought_fr_onlsearch

vaccination view
vacc_view_pos

### Independent Variables
 receive_i_fr_dr   
receive_i_fr_pers      
receive_i_fr_tv    
receive_i_fr_onlnet    
receive_i_fr_onlgroup

age 
gender 
race_white   
race_black    
race_nat      
race_asian 
hispanic
college

I received a $7,193 grant from the Summer Institute of Computational Social
Science to conduct research on network activation. Because I am co-PI on this
grant with my colleague Nicolas Legewie (University of Pennsylvania,
Humboldt-University of Berlin), I established permissions early-on in our
planning process to introduce and ‘own’ a few specific survey questions for
independent research on network versus non-network information activation.

The majority of this survey is a replication of the survey conducted in Mario
Small’s Book, Someone to Talk To (2017). We aim to expand on Small’s finding
that people draw on much broader sources than “important people” for support by
investigating how this theory of weak-tie support holds for different support
types (instrumental, emotional, and informational support; (see House et al.
1988)).

We aim to conduct surveys with 900 participants. The sample population for our
main survey are adult, non-institutionalized US residents. To adjust for the
non-representative sample provided by Amazon Mechanical Turk where we will host
the survey, we will use post-stratification weights based on the demographic
profile of each respondent (Wang et al. 2015).

@@

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, Black` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Some College, or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")))
```

@@

datasummary(formula = ((`Income` = income)+  
                         (`Gender` = gender)+  
                         (`Highest Education Level` = educ) + 
                         (`Plan to be Vaccinated if not` = vacc_status_future)  +
                         (`Found Info Sought Useful` = int_sought_useful)) ~ N + Percent(), 
 data = rain,
   fmt = '%.2f',
  title = 'Descriptive Statistics for Categorical Variables',
 notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

@@

```{r clean_before_reg}
rain <- rain %>% 
  mutate(across(c(receive_i,
                  receive_i_fr_dr,
                  receive_i_fr_pers,
                  receive_i_fr_tv,
                  receive_i_fr_onlnet,
                  receive_i_fr_onlgroup,
                  int_sought,
                  int_sought_fr_pers,
                  int_sought_fr_dr,
                  int_sought_fr_onlgroup,
                  int_sought_fr_onlnet,
                  int_sought_fr_onlsearch,
                  int_sought_affect,
                  vacc_status,
                  vacc_view_pos,
                  hispanic,
                  race_white,
                  race_black,
                  race_nat,
                  race_asian, 
                  college), ~ factor(.x, levels = c(1, 0))))

regression_labels = c(
  'receive_i_fr_dr0' = 'Received Info, Doctor',
  'receive_i_fr_pers0' = 'Received Info, Person',
  'receive_i_fr_tv0' = 'Received Info, News',
  'receive_i_fr_onlnet0' = 'Received Info, Social Networking Site',
  'receive_i_fr_onlgroup0' = 'Received Info, Online Forum',
  'int_sought0' = 'Sought Info',
  'int_sought_fr_dr0' = 'Sought Info, Doctor',
  'int_sought_fr_pers0' = 'Sought Info, Person',
  'int_sought_fr_onlnet0' = 'Sought Info, Social Networking Site',
  'int_sought_fr_onlgroup0' = 'Sought Info, Online Forum',
  'int_sought_fr_onlsearch0' = 'Sought Info, Online Search',
  'age' = 'Age',
  'gender=Male' = 'Gender, Male',
  'gender=Other' = 'Gender, Other',
  'college0' = 'Some College +',
  'race_white0' = 'White',
  'race_black0' = 'Black',
  'race_nat0' = 'Native American',
  'race_asian0' = 'Asian',
  'hispanic0' = 'Hispanic or Latino/x')
```

@@

modelsummary(mod1,
            gof_omit = 'AIC',
            # stars = TRUE,
            estimate = "{estimate}{stars}",
            title = 'What predicts someone intentionally searched for information',
            coef_map = regression_labels,
            notes = 'Exponentiated Coefficients',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

@@

Q172 How did you look for information about the Covid-19 vaccine?

*	Asking a person like friend, neighbor, or family member that I know  
*	Asking my doctor or another health professional  
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  
*	Searched for my question using an online search engine such as Google or Bing   
*	Other ________________________________________________

@@

modelsummary(part2_models,
             estimate = "{estimate}{stars}",
            gof_omit = 'AIC',
            coef_map = regression_labels,
            notes = 'Note: Exponentiated Coefficients',
            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')

# TODO ADD IN N To TABLE

@@

modelsummary(mod3,
            gof_omit = 'AIC',
            estimate = "{estimate}{stars}",
            title = 'Does receiving or searching for information predict vaccination status?',
            notes = 'Note: Exponentiated Coefficients',
            coef_map = regression_labels,
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = 'HOLD_position')
```

@@

plot_summs(mod3,
           scale = TRUE,
           coefs =  c(
             'Received Info, Doctor' = 'receive_i_fr_dr',
             'Received Info, Person' = 'receive_i_fr_pers',
             'Received Info, News' = 'receive_i_fr_tv',
             'Received Info, Social Networking Site' = 'receive_i_fr_onlnet',
             'Received Info, Online Forum' = 'receive_i_fr_onlgroup',
             'Sought Info' = 'int_sought',
             'Sought Info, Doctor' = 'int_sought_fr_dr',
             'Sought Info, Person' = 'int_sought_fr_pers',
             'Sought Info, Social Networking Site' = 'int_sought_fr_onlnet',
             'Sought Info, Online Forum' = 'int_sought_fr_onlgroup',
             'Sought Info, Online Search' = 'int_sought_fr_onlsearch',
             'Age' = 'age',
             'Gender, Male' = 'gender=Male',
             'Gender, Other' = 'gender=Other',
             'Some College +' = 'college',
             'White' = 'race_white',
             'Black' = 'race_black',
             'Native American' = 'race_nat',
             'Asian' = 'race_asian',
             'Hispanic or Latino/x' = 'hispanic'),
           robust = TRUE) +
  labs(title = 'Does receiving or searching for information predict vaccination status?', 
       caption = 'Coefficients Scaled and robust') +
  theme_diss()

@@

# Bibliography

# Appendix 1: Survey Questions

@@

@@

*	your doctor or other health professional?   (1) 
*	a person like friend, neighbor, or family member that you know ?  (9) 
*	From television news channel or the newspaper?  (10) 
*	From an online discussion group, listserve, or other online forum including a Facebook group or subreddit?  (11) 
*	From a social networking site such as Facebook timeline, Twitter status update, or linkedin?  (12) 
*	Other  (13) ________________________________________________

@@

*	Asking a person like friend, neighbor, or family member that I know  (1) 
*	Asking my doctor or another health professional  (4) 
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  (5) 
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  (6) 
*	Searched for my question using an online search engine such as Google or Bing  (7) 
*	Other  (8) ________________________________________________

*Q173*: What sort of information did you search for? 
 Separate different topics with a comma or semi-colon. 
___________

@@

*	Male  (1) 
*	Female  (2) 
*	Other  (3) ________________________________________________
*	Prefer not to say  (4)

@@

________________________________________________________________

>>>>

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, rms, modelsummary, showtext,thematic, kableExtra, scales)

@@

conf_int_prop <- function(var){
  p <- mean(!!var, na.rm = T)
  q <- 1 - p
  n <- nrow(rain)
  min <- p - 1.96*sqrt((p*q)/n)
  max <- p + 1.96*sqrt((p*q)/n) 
  paste0(round(min, 2), ", ", round(max, 2))
}

print_perc <- function(var){
  label_percent()(mean(var, na.rm = T))
}

side_by_side <- function(models, ...) {
    estimates <- c("Coef." = "{estimate}{stars}", 
                       "Std.Error" = "({std.error})")
    models <- rep(models, each = length(estimates))
    estimates <- rep(estimates,
                     times = length(models)/length(estimates))

    alignment <- paste(rep('l', length(models) + 1), collapse = '')

    names(models) <- names(estimates)

    modelsummary(models = models, 
                 estimate = estimates,
                 statistic = NULL,
                 align = alignment, ...)
}
```

# Intro
It is unclear how individuals choose to search for information through the
multimedia environment of the 21st century. Much of the research conducted in
social networks and communication focus on senders, influencers, and persuasion
strategies [@mertonManifestLatentFunctions1968] rather than on “the receiver as
an active information seeker and processor."
[@johnsonComprehensiveModelCancerRelated1993].

Core discussion networks are the default lens to investigate network resources
and social support in surveys. The underlying assumption is that individuals
reach out to a handful of strong ties when in need of support, which can be
elicited in surveys using name generators [@marsdenCoreDiscussionNetworks1987].
This approach has yielded important insights, but largely overlooks crucial
processes of resource activation [@hurlbertCoreNetworksTie2000;
@perrySocialNetworkActivation2015; @smithDonPutMy2005]. Small
[-@smallSomeoneTalk2017] shows that the core discussion network does not capture
how people activate social support in practice and indicates that people draw on
much broader social connections for support, also calling back to the weak ties
research by Granovetter [-@granovetterStrengthWeakTies1973]. There is ongoing
research investigating how weak-tie support holds for different support types
based on the architecture put forward by House, Umberson, and Landis
[-@houseStructuresProcessesSocial1988] of instrumental, emotional, and
informational support. I follow the definition of Cohen and Wills
[-@cohenStressSocialSupport1985] and define informational support as “help in
defining, understanding,  and coping with problematic events and include
education, advice, or referral to another source of  support”
[@winemillerMeasurementStrategiesSocial1993, p. 640].

However, informational support can also be sought outside of the social network
context, namely via computer-mediated information search tools such as the
process of “Googling”. As the online environment began penetrating all facets of
modern human life, it makes sense that performing online search has become one
*f the most convenient vehicles for information search. While Small
[-@smallSomeoneTalk2017] focuses on how support can depend on a network tie
simply "happened to be there", online search is theoretically the most
frictionless and costless mode of support. There are three computer-mediated
vehicles I consider for this analysis: search engines like Google, posting
questions on online forums like subreddits or Facebook groups, and posting a
status update online via Facebook or Twitter. The first two comprise what I call
“online search”, while the third is conceptually distinct and important to
include in the survey; yet, it is a hybrid of social network activation and
online search.

@@

For this paper, I will use the case of Covid-19 vaccinations to explore the
variation among information search vehicles. There are theoretical reasons why
individuals would choose to search for information among their network ties
instead of online search. For instance, Rains
[-@rainsCopingIllnessDigitally2018] finds that patients tend to search for
technical information about an illness online but turn to their social network
for experiential information from others facing similar circumstances in the
case of cancer. Moreover, if an individual distrusts the medical establishment,
or popular media, they may be more likely to activate informational support
among their social network or turn to online groups that validate their
worldview [@bogersHowSocialAre2014].

This research project is important because the vehicles used to search by people
impacts the information they are exposed to. Given the large swaths of both
misinformation and disinformation regarding Covid-19 [@mottaHowRightLeaningMedia2020; @pathakInfodemicsCOVID19Role2020; @shahsavariConspiracyTimeCorona2020] and
the measurable impacts this misinformation has had on pandemic-related health
behaviors, how we choose to search for information affects our own lives and the
lives of others. Moreover, individuals who do not utilize social networks for
information search may feel like they have no network support, leading to
feelings of network isolation with major implications for mental health 
[@thoitsMechanismsLinkingSocial2011]

@@

# Research Methodology
The data used for this research project are based on original survey data
sampled between `r format( min(rain$date), '%B %d, %Y')`  through 
`r format(max(rain$date), '%B %d, %Y')`. This survey was hosted on Qualtrics and
participants were paid and recruited using Amazon Turk (MTurk). The total valid
survey responses (n = `r nrow(rain)`) were selected from a total of 1,066
respondents; some responses were disqualified due to a few factors such as
detected usage of a VPN, random answer clicking (determined by illogical
responses), poor quality typed responses (e.g. social network alters
consistently named random nouns), or taking the survey more than once. The same
is slighted gender unbalanced, slightly skewing towards a male sample. For the
respondents who provided their zipcode (p = 
`r round(nrow(rain[!is.na(rain$region),]) / nrow(rain), 2)`), the 
sample is quite balanced with a slight skew towards MTurkers in the South (p = 
`r round(nrow(rain[rain$region == 'South',]) / nrow(rain), 2)`). 
The survey took an average of `r round(mean(rain$duration), 2)` minutes with a 
standard deviation of `r round(sd(rain$duration), 2)` minutes. The shortest 
valid survey took `r round(min(rain$duration), 2)` minutes and the longest took 
`r round(max(rain$duration), 2)` minutes. Participants were paid \$6.00 for their 
time after Amazon administrative fees, funded by a Grant awarded to Kelsey E.
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social
Science and the Russell Sage Foundation. The main portion of this survey
replicates the book, Someone to Talk To [@smallSomeoneTalk2017] by expandingon
Small’s finding that people draw on much broader sources than “important people”
for support by segregating weak-tie social support into instrumental, emotional,
and informational support (see House et al. 1988)). The latter part of the
survey focuses on resource activation for the specific case-study of information
during the Covid-19 pandemic and is analyzed in this paper.

@@

datasummary(formula = 
  (`Received info` = receive_i) +
    (`Received info, Doctor` = receive_i_fr_dr) +
    (`Received info, Person` = receive_i_fr_pers) +
    (`Received info, News` = receive_i_fr_tv) +
    (`Received info, Social Networking Site` = receive_i_fr_onlnet) +
    (`Received info, Online Forum` = receive_i_fr_onlgroup) +
    (`Sought Info` = int_sought) +
    (`Sought Info, Doctor` = int_sought_fr_dr) +
    (`Sought Info, Person` = int_sought_fr_pers) +
    (`Sought Info, Social Networking Site` = int_sought_fr_onlnet) +
    (`Sought Info, Online Forum` = int_sought_fr_onlgroup) +
    (`Sought Info, Online Search` = int_sought_fr_onlsearch) +
    (`Vaccination Status` = vacc_status) +
    (`Vaccination Favorability` = vacc_view_pos) +
    (`Age` = age) +
    (`Hispanic or Latino/x` = hispanic) +
    (`Race, Black` = race_white) +
    (`Race, Black` = race_black) +
    (`Race, Native American` = race_nat) +
    (`Race, Asian or Pacific Islander` = race_asian) +
    (`Some College, or above` = college)  ~ 
    (Mean + SD) ,
  data = desc_table,
  fmt = '%.2f',
  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
  notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
  output = "kableExtra") %>% 
  kable_styling(latex_options = c("hold_position", "striped"))

## Measures

###  Sought Information
There are multiple dependent variables of interest for this paper. The first
variable is a dichotomous indicator of whether someone intentionally sought out
information about Covid-19 vaccinations. The survey asked, "And how about you 
yourself intentionally looking for information about a Covid-19 vaccine? Such 
information can include things such as advice, clarification, facts, and
experiences". About `r print_perc(rain$int_sought)` ($\widehat{p}$)
of respondents had intentionally sought out information about Covid-19 
vaccinations (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought)`\}).

Further dependent variables segment the above question into multiple options;
"How did you look for information about the Covid-19 vaccine?". Respondents were
posed with 5 responses and 'other', of which they could select multiple. The
largest proportion, `r print_perc(rain$int_sought_fr_dr)`, asked their 
'doctor or another health professional' (95% Confidence Interval = 
\{`r conf_int_prop(rain$int_sought_fr_dr)`\}).
About `r print_perc(rain$int_sought_fr_pers)`  said they asked 'a person 
like friend, neighbor, or family member that [they] know' (95% Confidence 
Interval = \{`r conf_int_prop(rain$int_sought_fr_pers)`\}). An additional
`r print_perc(rain$int_sought_fr_onlsearch)` searched 'for [their] question 
using an online search engine such as Google or Bing' (95% Confidence Interval 
= \{`r conf_int_prop(rain$int_sought_fr_onlsearch)`\}). About a quarter of the 
sample, `r print_perc(rain$int_sought_fr_onlgroup)`, 'posted queries in an 
online discussion group, listserve, or other online forum like a Facebook Group 
or Subreddit' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlgroup)`\}).
And finally, `r print_perc(rain$int_sought_fr_onlnet)` of the sample 'posted queries 
on a social networking site such as Facebook timeline, Twitter status update, or 
Linkedin' (95% Confidence Interval = \{`r conf_int_prop(rain$int_sought_fr_onlnet)`\}).
Much of the question wording and the specific categories of search were inspired
by ICPSR project 37220 [@scanlon19].

@@

datasummary(formula = (
  # (`Income` = income)+  
                         (`Gender` = gender)+  
                         (`Highest Education Level` = educ) + 
                         (`Plan to be Vaccinated if not` = vacc_status_future)  +
                         (`Found Info Sought Useful` = int_sought_useful) +
                         (`Census Region` = region)) ~ N + Percent(), 
 data = rain,
   fmt = '%.2f',
  title = 'Descriptive Statistics for Categorical Variables',
 notes =c(glue("Notes: {nrow(rain)} Surveyed, Conducted {format( min(rain$date), '%B %d')} through {format(max(rain$date), '%B %d')}, 2021.")),
 output = "kableExtra") %>%
  kable_styling(latex_options = c("hold_position", "striped"))

@@

### Vaccination Outlook

```{r}
vacc_status_freq <- rain[!is.na(rain$vacc_status_future),] %>% 
  group_by(col = vacc_status_future) %>% 
  summarise(n = n()) %>%
  mutate(n = n / sum(n))
```
Another Dependent variable for this analysis is a dichotomous variable
indicating whether the respondent has received a vaccination against Covid-19 or
plans to. For this survey, the number of doses were unimportant and actually
having already received the dose were irrelevant to the research question. This
variable instead focuses on intent or opinion about the vaccine. About 
`r print_perc(rain$vacc_view_pos)` have a positive view about the vaccine. This
construct is made through the combination of  two survey items. The first item
is actual vaccination status, obtained through the question 'Did you receive a
Covid-19 vaccine?'. `r print_perc(rain$vacc_status)` of the sample said that
they had indeed received a vaccination (95% Confidence Interval = \{
`r conf_int_prop(rain$vacc_status)`\}). As the national vaccination rate is
closer to 55% (CITE), this indicates some bias in our sample that must be
acknowledged: either MTurkers are more likely to be vaccinated that the normal
population (sampling bias) or there is some conformity bias in the responses
causing survey takers to provide false answers. The second survey item that
contributes to 'Vaccination Outlook' was only given to those who had not
responded 'yes' to the to their vaccination status. These respondents were asked 'Do you
plan to receive a vaccine for the prevention of the Covid-19 virus?'. Of those
who were asked this question (n = `r nrow(rain[!is.na(rain$vacc_status_future),])`),
`r label_percent()(filter(vacc_status_freq, col == 'Definitely yes') %>% pull(n))`
said they were 'definitely yes' getting the vaccine; 
`r label_percent()(filter(vacc_status_freq, col == 'Probably yes') %>% pull(n))` 
said they were 'probably yes' going to receive vaccine. The rest of the sample was more unsure: 
`r label_percent()(filter(vacc_status_freq, col == 'Might or might not') %>% pull(n))`
said they 'Might or might not', 
`r label_percent()(filter(vacc_status_freq, col == 'Probably not') %>% pull(n))`
said 'Probably not', and finally
`r label_percent()(filter(vacc_status_freq, col == 'Definitely not') %>% pull(n))`
said they would 'definitely not' receive the vaccine. The variable 'Vaccination
Outlook' indicates their either the respondent received a Covid-19 vaccine or
either probably or definitely will in the future.

### Independent Variables
The first independent variables used in this analysis are based on the question, 
'In the past 12 months, without searching for it, did you receive information
about the Covid-19 vaccine from … (check all sources you received information
from)'. This differs from the 'How did you look for information' question above
because it is based on passive reception of information. The largest proportion
of respondents had received information from a person like friend, neighbor, or
family member that [they] know ($\widehat{p}$ = `r print_perc(rain$receive_i_fr_pers)`
). Respondents also commonly received information from a television news channel
or a newspaper, about `r print_perc(rain$receive_i_fr_tv)` of the sample.
`r print_perc(rain$receive_i_fr_dr)` of the sample had received information from
their doctor or other health professional while `r print_perc(rain$receive_i_fr_onlnet)` 
received information from a social networking site such as Facebook timeline,
Twitter status update, or linkedin. Finally, the lowest proportion of the sample
had received information from an online discussion group, listserve, or other
online forum like a Facebook group or subreddit 
($\widehat{p}$ = `r print_perc(rain$receive_i_fr_onlgroup)`).

We also asked various demographic questions to understand our sample. The 
average age of our sample was `r round(mean(rain$age, na.rm = T), 2)`. 
Our sample was `r label_percent()(nrow(filter(rain, gender == "Female")) / nrow(rain))`
female, and `r label_percent()(nrow(filter(rain, gender == "Male")) / nrow(rain))`
male. The sample is diverse racially though some ethnic groups are under
represented compared to national averages. Race was evaluated using the
question, 'What is your race? If you are "mixed race", select all that apply.'
Because of the multi-selection question, each variable is dichotomous and
proportions are shown. `r print_perc(rain$race_white)` of the sample claimed
they were 'White', `r print_perc(rain$race_black)` claimed to be 'Black or
African American', `r print_perc(rain$race_nat)` chose 'American Indian or
Alaskan Native', `r print_perc(rain$race_asian)` selected 'Asian', and finally 
when asked ' Are you Hispanic, Latino/a/x, or Latin American Origin?', 
`r print_perc(rain$hispanic)` selected 'Yes'. Respondents were also asked to 
select the  highest level of education that you have completed. Based on the 
breakdown between 'Less than high school', 'High school graduate', 'Some college',
'Associate's or Technical degree', 'Bachelor's degree', and 'Graduate or 
professional degree',  `r print_perc(rain$college)` of the sample were classified
to have a College-level education (Associate's degree or above).

My analytic strategy proceeds in four steps. In Tables X & Y, I present descriptive
statistics for all study variables, including variable ranges, means, and standard
deviations.

In Table 3, I fit a model of state mobility scores using robust regression with the M estimator and iterated re-weighted least squares (IWLS) to downweight the influence of outliers (Jorgenson 2007; Venables and Ripley 2002). Model
1 regresses state mobility scores on dummy variables for week. This model tests
whether mobility scores vary across the 8-week study period. We use dummy variables for week to capture thresholds in the association between week and mobility.
Model 2 adjusts for state religiosity, median age, percent black, the unemployment
rate, population density, and the mobility lag. This model tests whether state religiosity is associated with state mobility scores net of state demographic characteristics

```{r clean_before_reg}
rain <- rain %>% 
  mutate(across(c(receive_i,
                  receive_i_fr_dr,
                  receive_i_fr_pers,
                  receive_i_fr_tv,
                  receive_i_fr_onlnet,
                  receive_i_fr_onlgroup,
                  int_sought,
                  int_sought_fr_pers,
                  int_sought_fr_dr,
                  int_sought_fr_onlgroup,
                  int_sought_fr_onlnet,
                  int_sought_fr_onlsearch,
                  int_sought_affect,
                  vacc_status,
                  vacc_view_pos,
                  hispanic,
                  race_white,
                  race_black,
                  race_nat,
                  race_asian, 
                  college), ~ factor(.x, levels = c(0, 1))))

regression_labels = c(
  'receive_i_fr_dr1' = 'Received Info, Doctor',
  'receive_i_fr_pers1' = 'Received Info, Person',
  'receive_i_fr_tv1' = 'Received Info, News',
  'receive_i_fr_onlnet1' = 'Received Info, Social Networking Site',
  'receive_i_fr_onlgroup1' = 'Received Info, Online Forum',
  'int_sought1' = 'Sought Info',
  'int_sought_fr_dr1' = 'Sought Info, Doctor',
  'int_sought_fr_pers1' = 'Sought Info, Person',
  'int_sought_fr_onlnet1' = 'Sought Info, Social Networking Site',
  'int_sought_fr_onlgroup1' = 'Sought Info, Online Forum',
  'int_sought_fr_onlsearch1' = 'Sought Info, Online Search',
  'age' = 'Age',
  'gender=Male' = 'Gender, Male',
  'gender=Other' = 'Gender, Other',
  'college1' = 'Some College +',
  'race_white1' = 'White',
  'race_black1' = 'Black',
  'race_nat1' = 'Native American',
  'race_asian1' = 'Asian',
  'hispanic1' = 'Hispanic or Latino/x')
```

@@

# mod1 = list(mod1)

# side_by_side(mod1, 
#              gof_omit = 'AIC',
#              title = 'What predicts someone intentionally searched for information',
#             coef_map = regression_labels,
#             notes = 'Exponentiated Coefficients',
#             exponentiate = TRUE,
#             output = "kableExtra") %>%
#   kable_styling(latex_options = c("HOLD_position", "striped"))

modelsummary(mod1,
            gof_omit = 'AIC', statistic = NULL,
            estimate = "{estimate}{stars} ({std.error})",
            title = 'What predicts someone intentionally searched for information',
            coef_map = regression_labels,
            notes = 'Exponentiated Coefficients',
            exponentiate = TRUE,
 output = "kableExtra") %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))

@@

@@

modelsummary(part2_models,
             align="llllll",
             statistic = NULL,
            estimate = "{estimate}{stars}",
            gof_omit = 'AIC',
            coef_map = regression_labels,
            notes = 'Note: Exponentiated Coefficients',
            title = 'What predicts someone intentionally searched for information, by vehicle of information search',
            exponentiate = TRUE,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("scale_down", "HOLD_position", "striped"))  %>%
  add_header_above(c(" " = 1, "Dependent Variable" = 5))

# 
# 
# 
# 
# side_by_side(part2_models, 
#              gof_omit = 'AIC',
#             coef_map = regression_labels,
#             notes = 'Note: Exponentiated Coefficients',
#             title = 'What predicts someone intentionally searched for information, by vehicle of information search',
#             exponentiate = TRUE,
#             output = "kableExtra") %>%
#   kable_styling(latex_options = c("HOLD_position", "striped")) %>% 
#   add_header_above(c(" ", 
#                      "Person" = 2,
#                      "Doctor" = 2, 
#                      "Online Forum" = 2,
#                      "Social Networking\nSite" = 2,
#                      "Online Search"  = 2)) %>%
#   add_header_above(c(" " = 1, "Dependent Variable" = 10)) %>%
#   kableExtra::landscape()

@@

# 
# mod3 = list(mod3)
# 
# 
# side_by_side(mod3, 
#              gof_omit = 'AIC',
#             title = 'Does receiving or searching for information predict vaccination status?',
#             notes = 'Note: Exponentiated Coefficients',
#             coef_map = regression_labels,
#             exponentiate = TRUE,
#             output = "kableExtra") %>%
#   kable_styling(latex_options = c("HOLD_position", "striped"))
#

modelsummary(mod3,
            gof_omit = 'AIC', statistic = NULL,
            estimate = "{estimate}{stars} ({std.error})",
            title = 'Does receiving or searching for information predict vaccination status?',
            notes = 'Note: Exponentiated Coefficients',
            coef_map = regression_labels,
            exponentiate = TRUE,
            output = "kableExtra") %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

@@

plot_summs(mod3,
           scale = TRUE,
           coefs =  c(
             'Received Info, Doctor' = 'receive_i_fr_dr',
             'Received Info, Person' = 'receive_i_fr_pers',
             'Received Info, News' = 'receive_i_fr_tv',
             'Received Info, Social Networking Site' = 'receive_i_fr_onlnet',
             'Received Info, Online Forum' = 'receive_i_fr_onlgroup',
             'Sought Info' = 'int_sought',
             'Sought Info, Doctor' = 'int_sought_fr_dr',
             'Sought Info, Person' = 'int_sought_fr_pers',
             'Sought Info, Social Networking Site' = 'int_sought_fr_onlnet',
             'Sought Info, Online Forum' = 'int_sought_fr_onlgroup',
             'Sought Info, Online Search' = 'int_sought_fr_onlsearch',
             'Age' = 'age',
             'Gender, Male' = 'gender=Male',
             'Gender, Other' = 'gender=Other',
             "Associate's Deg or above" = 'college',
             'White' = 'race_white',
             'Black' = 'race_black',
             'Native American' = 'race_nat',
             'Asian' = 'race_asian',
             'Hispanic or Latino/x' = 'hispanic'),
           robust = TRUE) +
  labs(title = 'Does receiving or searching for information predict vaccination sentiment?', 
       caption = 'Coefficients Scaled and robust') +
  theme_diss()

@@

\newpage
# References {-}

<div id="refs"></div>

\newpage
# Appendix 1: Survey Questions

-------------------------------------------------

@@

-------------------------------------------------

@@

*	your doctor or other health professional?   (1) 
*	a person like friend, neighbor, or family member that you know ?  (9) 
*	From television news channel or the newspaper?  (10) 
*	From an online discussion group, listserve, or other online forum including a Facebook group or subreddit?  (11) 
*	From a social networking site such as Facebook timeline, Twitter status update, or linkedin?  (12) 
*	Other  (13) _______

-------------------------------------------------

@@

*	Asking a person like friend, neighbor, or family member that I know  (1) 
*	Asking my doctor or another health professional  (4) 
*	Posted queries in an online discussion group, listserve, or other online forum like a Facebook Group or Subreddit  (5) 
*	Posted queries on a social networking site such as Facebook timeline, Twitter status update, or Linkedin  (6) 
*	Searched for my question using an online search engine such as Google or Bing  (7) 
*	Other  (8) ___________

-------------------------------------------------

*Q173*: What sort of information did you search for? 
 Separate different topics with a comma or semi-colon.

-------------------------------------------------

@@

*	Male  (1) 
*	Female  (2) 
*	Other  (3) ________________
*	Prefer not to say  (4)

-------------------------------------------------

@@
